---
title: "p8105_hw1_dn2501"
author: David Nemirovsky
date: 9/16/20
output: github_document
---

This is my solution to HW1:

```{r load tinyverse, collapse = TRUE}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements.

```{r creating a df, collapse = TRUE}
Prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high")
)
```

Take the mean of each variable in my data frame.

```{r means, collapse = TRUE}
mean(pull(Prob1_df, samp))
mean(pull(Prob1_df, samp_gt_0))
mean(pull(Prob1_df, char_vec))
mean(pull(Prob1_df, factor_vec))
```

I am able to take the mean of numbers/logical vectors but not characters/factors.

```{r converting variables, eval = FALSE}
as.numeric(pull(Prob1_df, samp_gt_0))
as.numeric(pull(Prob1_df, char_vec))
as.numeric(pull(Prob1_df, factor_vec))
```

This function is able to convert the logical variable to values of 0 and 1, however, it resulted in vectors of NA for the character and factor variables. This could be because R has no way of assigning numeric values to character/factor values, therefore a mean of these cannot be computed.

```{r more converting, collapse = TRUE}
as.numeric(pull(Prob1_df, samp_gt_0)) * pull(Prob1_df, samp)
as.factor(pull(Prob1_df, samp_gt_0)) * pull(Prob1_df, samp)
as.numeric(as.factor(pull(Prob1_df, samp_gt_0))) * pull(Prob1_df, samp)
```

Instead of converting the logical vector into a numeric with values of 0 and 1, I was able to first convert the logical vector into a factor, and then the factor vector into a numeric, resulting in values of 1 and 2 for the original logical vector; giving more meaning to its scaling of the sample.


##Problem 2

```{r descriptive summary of penguins data set, results = 'hide'}
library(palmerpenguins)
data("penguins", package = "palmerpenguins")
summary(penguins)
nrow(penguins)
ncol(penguins)
is.na(pull(penguins, flipper_length_mm))
na.omit(pull(penguins, flipper_length_mm))
mean(na.omit(pull(penguins, flipper_length_mm)))
```

The "penguins" data set is composed of variables of penguins indicating their species, island of residency, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex, and the year the data was recorded. This data set has `r nrow(penguins)` rows and `r ncol(penguins)` columns. The mean flipper length of penguins in this data set is `r mean(na.omit(pull(penguins, flipper_length_mm)))` mm.


