---
title: "p8105_hw1_dn2501"
author: David Nemirovsky
date: 9/16/20
output: github_document
---

This is my solution to HW1:

```{r}
library(tidyverse)
```

## Problem 1

Create a data frame with the specified elements.

```{r creating a df}
Prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high")
)
```

Take the mean of each variable in my dat frame.

```{r means}
mean(pull(Prob1_df, samp))
mean(pull(Prob1_df, samp_gt_0))
mean(pull(Prob1_df, char_vec))
mean(pull(Prob1_df, factor_vec))
```

I am able to take the mean of numbers/logical but not characters/factors.

```{r converting variables, message= FALSE}
as.numeric(pull(Prob1_df, samp_gt_0))
as.numeric(pull(Prob1_df, char_vec))
as.numeric(pull(Prob1_df, factor_vec))
```

This function is able to convert the logical variable to values of 0 and 1, however, it resulted in vectors of NA for the character and factor variables. This could be because R has no way of assigning numeric values to character/factor values, therefore a mean of these cannot be computed.

```{r more converting}
as.numeric(pull(Prob1_df, samp_gt_0)) * pull(Prob1_df, samp)
as.factor(pull(Prob1_df, samp_gt_0)) * pull(Prob1_df, samp)
as.numeric(as.factor(pull(Prob1_df, samp_gt_0))) * pull(Prob1_df, samp)
```

Instead of converting the logical vector into a numeric with values of 0 and 1, I was able to first convert the logical vector into a factor, and then the factor vector into a numeric, resulting in values of 1 and 2 for the original logical vector; giving more meaning to its scaling of the sample.


##Problem 2

